--- 
title: "數量方法（一）"
author: "林茂廷老師"
date: "`r Sys.Date()`"
description: 數量方法（一）電子書
documentclass: ctexbook
geometry:
- b5paper
- tmargin=2.5cm
- bmargin=2.5cm
- lmargin=3.5cm
- rmargin=2.5cm
link-citations: yes
lof: yes
lot: yes
site: bookdown::bookdown_site
colorlinks: yes
---

```{r setup, include=FALSE}
options(
  htmltools.dir.version = FALSE, formatR.indent = 2, width = 55, digits = 4
)

lapply(c(), function(pkg) {
  if (system.file(package = pkg) == '') install.packages(pkg)
})

knitr::opts_chunk$set(message=FALSE,
                      echo=FALSE,
                      fig.showtext=TRUE)
library(showtext)
showtext_auto()
```

# 課程大綱 {-}  

電子書網址：<https://bookdown.org/tpemartin/econometric_analysis/>

## 基本資訊 {-}   
授課老師： 林茂廷  
辦公室：社科大樓3F01  
諮詢時間：週二下午2點30-4點30     
電話：02﹣86741111轉67170  
Email：mtlin@gm.ntpu.edu.tw   
作業上傳網址：https://www.dropbox.com/request/wAzlAatjCjvvExQZlzje  
課程討論室：https://sites.google.com/view/econometric-analysis/home  
分組名單填寫網址：https://goo.gl/forms/zXymIEOQbgagwRkg2
分組結果：[請點此查閱自己的"組號"](https://docs.google.com/spreadsheets/u/2/d/e/2PACX-1vRj0T659dEfUuxUJYpWumtP0OdYIbCgP6xV6O_SXeYFK6SZtUz8b6RXdf7eLe6CZK_u7IRtay5-QR2Y/pubhtml?gid=860068219&single=true)  
課堂程式說明：[Github repo: Econometrics-in-class-practice](https://github.com/tpemartin/Econometrics-in-class-practice)

## 主題內容 {-}  
In this semester, we will focus on Part II and Part VI of Greene’s book. The topics that I will cover are:

[1] The Generalized Regression Model (ch.8)  
[2] Models for Panel Data (ch.9)  
[3] Models for Discrete Choice (ch.23)  
[4] Truncation, Censoring, and Sample Selection (ch.24)  
[5] Instrumental Variable Estimation (ch.12)  

## 參考書籍 {-}  
- Greene, William, Econometric Analysis, 6th ed, 2007, Prentice Hall. 
- [R for Data Science](http://r4ds.had.co.nz/).  
- [Principles of Econometrics with R](https://bookdown.org/ccolonescu/RPoE4/), Constantin Colonescu, bookdown.org, 2016.  
- [Efficient R Programming](https://bookdown.org/csgillespie/efficientR/), Colin Gillespie and 
Robin Lovelace, bookdown.org, 2016.  
- [Econometrics with R](https://econometricswithr.wordpress.com/), Franz Mohr, personal blog (Awesome!!! I must say.)

## Cheatsheets {-}  
- [dplyr](https://github.com/rstudio/cheatsheets/raw/master/data-transformation.pdf)  
- [R markdown](https://github.com/rstudio/cheatsheets/raw/master/rmarkdown-2.0.pdf)  
- [ggplot2](https://github.com/rstudio/cheatsheets/raw/master/data-visualization-2.1.pdf)  

## 本學期上課前請先依序完成以下項目 {-}  
1. 安裝：R and R Studio Desktop: https://www.rstudio.com  
2. 註冊Github.com: https://www.github.com  
3. 安裝Github desktop: https://desktop.github.com/
4. 連到<https://gitter.im>用你的Github帳號登錄。
5. 註冊hypothes.is: <https://hypothes.is>  
6. 填寫課程資料: <https://goo.gl/hZzv4D>

## hypothes.is電子講義討論群 {-}  
- <https://hypothes.is/groups/xPgdmzMj/shu-fang-106xue-nian>  


<!--
分組
Study Group
3 to 5 people form a study group. Once it is decided, visit the google document website that I will send to you later to fill in your group number. Please chose a number from 1 to 10 as a group ID to represent your group. Don’t choose the same number as other groups.
-->

## 評分方式 {-}
方案一：  
```{r}
library(ggplot2)
library(dplyr)
library(magrittr)
assessment<-data.frame(
  type=c("課堂參與","作業","期中考","期末考"),
  percentage=c(10,20,30,40))


# Simple Pie Chart
assessment %$%
pie(percentage, labels = paste0(type," ", percentage,"%",sep=""), family="wqy-microhei")
```

方案二：
不超過3人（限本課程同學）參加[2018經濟部落客競賽](https://ntpuecon.github.io/econblogcompetition/)

```{r}
library(ggplot2)
library(dplyr)
library(magrittr)
assessment<-data.frame(
  type=c("課堂參與","作業","期中考","期末考","競賽"),
  percentage=c(10,20,30,30,10))


# Simple Pie Chart
assessment %$%
pie(percentage, labels = paste0(type," ", percentage,"%",sep=""), family="wqy-microhei")
```

